Non-word repetition in children learning Yélî Dnye

### 2021-10-27 manuscript.Rmd
version ready for proofing

keywords          : "phonology, non-word repetition, Papuan, non-industrial, non-urban, comparative, typology, markedness, literacy"
wordcount         : "~11,500 words"

@@

sink("lastknit_session_info.txt")
sessionInfo()
sink()
```

@@

Our focus on age stems from previous work, where performance increases with child age [@farmani2018normalization; @kalnak2014nonword; @vance2005speech]. Although past research has not investigated potential correlations with birth order on NWR, there is a sizable literature on these correlations in other language tasks [e.g., @havron2019effect], and therefore we report on these too. Common explanations for advantages for first- over later-born children include differential allocation of familial resources, particularly parental behaviors of cognitive stimulation [@lehmann2018early]. Regarding child sex, no significant correlation has been found in previous NWR research [@chiat2007preschool], and in other language tasks evidence is mixed. Finally, prior research varies on whether significant differences as a function of  maternal education are reported [e.g., no difference found in @farmani2018normalization; @kalnak2014nonword; @meir2017independent; @balladares2016socio; whereas differences were reported in @tuller2018identifying; @dos2020epreuve]. In other lines of work, maternal education correlates with child language outcomes, including vocabulary reports [@frank2017wordbank] and word comprehension studies [@scaff2019]. The causal pathways explaining this correlation are complex, but one explanation that is often discussed involves more educated mothers talking more to their children [see discussion in @cristia2020infant].

@@

Some general ideas regarding potential correlations between our NWR measures and maternal education may be drawn from the observations above. To begin with, many of our participants above 6 years of age may not be living with their birth mother but with other relatives, which may weaken associations with maternal education. 
<!-- Additionally, the importance given to formal education appears relatively stable over the period that Rossel Island has been visited by language researchers (Steven Levinson and Penelope Brown, about 20 years). ac2mc removed, R was confused and I'm also not sure what is the relevance of this comment

mc2ac: fine with me, thanks!-->
In addition, it seems to us that the length of formal education a given individual may have is not necessarily a good index of their socio-economic status or other individual properties, unlike what happens in industrialized sites, and variation may simply be due to random factors like living close to a school or having relatives there.

@@

<!-- ac2mc shouldn't we totally rewrite this? // actually, this is all factually correct-->
<!-- mc2ac: while factually correct i thought it might not be a great representation of where we stand now so i made some small edits in the final sentences-->
We add some observations that will help us integrate this study into the broader investigation of NWR across cultures. As mentioned previously, there is one report of relatively low NWR scores among the Tsimane', which the authors of that paper interpret as consistent with long-term effects of low levels of infant-directed speech [@cristia2020infant]. However, @cristia2020infant also point out that this is based on between-paper comparisons, and thus methods and myriad other factors have not been controlled for. The Yélî community can help us gain new insights into this matter because direct speech to children under 3;0 is comparably infrequent in this community [in fact it may be infrequent in many settings, including urban ones @bunceURcrosscultural], and additionally shares other societal characteristics wih the Tsimane' [e.g., is rural and relies on farming, children grow up in wide familial networks, etc; @casillas2021early]. Although infant-directed speech has been measured in different ways among the Tsimane' and the Yélî communities, our most comparable estimates at present suggest that Tsimane' young children are spoken to about 4.2 minutes per hour [@scaff2021daylong], and Yélî children about 3.6 minutes per hour [@casillas2021early]. Thus, if these input quantities in early childhood relate to lower NWR scores later in life, we should observe similarly low NWR scores here as in @cristia2020infant.

@@

kable(stims.wide,
  "latex", booktabs = T,
  caption="NWR stimuli in orthographic (Orth.) and phonological (Phon.) representations.",
  row.names =F) %>%
  kable_styling() %>%
  add_header_above(c("Practice" = 2, "Monosyll" = 2,
    "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))

@@

The first author then annotated the onset and offset of all children's productions from the audio recording using Praat audio annotation software [@Praat], then ran a script to extract these tokens, pairing them with their original auditory target stimulus, and writing these audio pairs out to .wav clips. The assistant then listened through all these paired target-repetition clips randomized across children and repetitions, grouped such that all the clips of the same target were listened to in succession. For each clip, the assistant indicated in a notebook whether the child production was a correct or incorrect repetition and orthographically transcribed the production, noting when the child uttered a recognizable word or phrase and adding the translation equivalent of that word/phrase into English. The assistant was also provided with some general examples of the types of errors children made without making specific reference to Yélî sounds or the items in the elicitation sets. Because the phonological inventory is so acoustically packed and because annotation was done based on audio data alone, it might be easy to mis-identify a segment, the assistant double-checked all of her annotations by listening to them and assessing them a second time, once she had completed a full first round.

@@

item.plot <- ggplot(data = xling, aes(x = Avg_fr, y = Word, label = phono)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  geom_text(family = "Doulos SIL") +
  ylab("NWR scores (% words)") +
  xlab("Average cross-linguistic phone frequency") +
  theme_apa()
ggsave("nwr.by.freq.ITEM.png", dpi = 300, device = png())
knitr::include_graphics("nwr.by.freq.ITEM.png")
dev.off()
```

Additionally, the effect for the interaction between the two fixed effects was small but significant (ß = `r mycoeff["avg_fr_s:age.rounded_s","Estimate"]`, SE ß = `r mycoeff["avg_fr_s:age.rounded_s","Std. Error"]`, p `r pval.display(mycoeff["avg_fr_s:age.rounded_s","Pr(>|z|)"])`): The effect of frequency was larger for younger children. Inspection of Figure \@ref(fig:fig-xling-freq-age3) suggests that the age effects are more marked for items containing cross-linguistically common phones, such that children's average performance increases more rapidly with age for those than for items containing cross-linguistically uncommon phones.

```{r fig-xling-freq-age3, fig.pos = "!t", fig.align = "center", out.width = '65%', fig.cap="Model predicting NWR scores from child age (x axis) and the average frequency with which each phone is found across languages (mean, or plus/minus one standard deviation)."}

@@

plot_model(xl_fr, type = "pred", terms = c("age.rounded_s","avg_fr_s")) +
  geom_point(data = trnsc.inc.indivs, inherit.aes = FALSE,
             aes(x = age.rounded_s, y = correct, color = factor(avg_fr_s))) +
  scale_color_manual(values = c("red", "orange", "green"),
                     labels = c("mean - 1sd", "mean", "mean + 1sd")) +
  scale_fill_manual(values = c("red", "orange", "green"),
                    guide = FALSE) +
  labs(color = "Avgerage\nfrequency\nscore",
       y = "% Correct", x = "Child age\n(standardized)") +
  theme_apa() +
  theme(plot.title = element_blank(),
        legend.key = element_rect(color = "white")) +
  guides(color = guide_legend(override.aes = list(fill = NA), reverse = TRUE))

@@

<!-- ac2mc if it's easy for you to add dots representing actual children in the above, that would be awesome! If not, I can try to tackle it :)

mc2ac here's my attempt! i wasn't sure how you wanted to aggregate the real data to correspond to the model estimates so i have here grouped correctness within individual by
<= m - 1sd
mean <±> 1sd (unconventional notation, sorry)
>= m + 1sd

if you had something else in mind but are otherwise cool with the figure, it should be easy to edit on the mutate/case_when() portion defining trnsc.inc.indivs
-->

@@

#read.table("substitution_bank_try1.txt",header=T)->sub_bank
read.table("substitution_bank.txt",header=T)->sub_bank_full
sub_bank=sub_bank_full[,1:2]
sub_bank$target=factor(sub_bank$target,levels=allVC)
sub_bank$realization=factor(sub_bank$realization,levels=allVC)

@@

#read.table("deletion_bank_try1.txt",header=T)->del_bank
read.table("deletion_bank.txt",header=T)->del_bank_full
del_bank=del_bank_full[,1]
del_bank=factor(del_bank,levels=allVC)
del_tab= table(del_bank)[allVC]

#read.table("match_bank_try1.txt",header=T)->match_bank
read.table("match_bank.txt",header=T)->match_bank_full
match_bank=match_bank_full[,1]
match_bank=factor(match_bank,levels=allVC)
match_tab= table(match_bank)[allVC]

@@

We do not have the necessary data to assess whether the correlation is indeed weaker for Yélî Dnye learners than learners of other languages, but we did find a robust correlation of average segmental cross-linguistic frequency and NWR performance: Even accounting for age and random effects of item and participant, we saw that target words with typologically more common segments were repeated correctly more often. This effect was large, with a magnitude more than twice the size of the effect of participant age. Additionally, we observed an interaction between age and this factor, which emerged because cross-linguistic frequency explained more variance at younger ages (i.e., the difference in performance for more versus less typologically frequent sounds was greater for younger than older children). Importantly, the correlation between performance and typological frequency  remained significant  after accounting for the frequencies of these segments in a conversational corpus. An analysis of the substitutions made by children also aligned with this interpretation, with typologically more common sounds being substituted for typologically less common ones.

>>>>

keywords          : "phonology, non-word repetition, Papuan, non-industrial, non-urban, comparative, typology, markedness, literacy"
wordcount         : "~12,200 words"

@@

writeLines(capture.output(sessionInfo()), "lastknit_session_info.txt")

#missing compared to MC
# compiler_4.1.1
# AC has xfun_0.27 , MC has xfun_0.26
# ac has rlang_0.4.12, mc has rlang_0.4.11
```

@@

Our focus on age stems from previous work, where performance increases with child age [@farmani2018normalization; @kalnak2014nonword; @vance2005speech]. Although past research has not investigated potential correlations with birth order on NWR, there is a sizable literature on these correlations in other language tasks [e.g., @havron2019effect], and therefore we report on these too. Common explanations for advantages for first- over later-born children include differential allocation of familial resources, particularly parental behaviors of cognitive stimulation [@lehmann2018early]. Regarding child sex, no significant correlation has been found in previous NWR research [@chiat2007preschool], and in other language tasks evidence is mixed. Finally, prior research varies on whether significant differences as a function of  maternal education are reported. For instance, no significant difference was found some studies [@farmani2018normalization; @kalnak2014nonword; @meir2017independent; @balladares2016socio]; whereas significant differences were reported in others [@tuller2018identifying; @dos2020epreuve]. In other lines of work, maternal education correlates with child language outcomes, including vocabulary reports [@frank2017wordbank] and word comprehension studies [@scaff2019]. The causal pathways explaining this correlation are complex, but one explanation that is often discussed involves more educated mothers talking more to their children [see discussion in @cristia2020infant].

@@

Some general ideas regarding potential correlations between our NWR measures and maternal education may be drawn from the observations above. To begin with, many of our participants above 6 years of age may not be living with their birth mother but with other relatives, which may weaken associations with maternal education. 
In addition, it seems to us that the length of formal education a given individual may have is not necessarily a good index of their socio-economic status or other individual properties, unlike what happens in industrialized sites, and variation may simply be due to random factors like living close to a school or having relatives there.

@@

We add some observations that will help us integrate this study into the broader investigation of NWR across cultures. As mentioned previously, there is one report of relatively low NWR scores among the Tsimane', which the authors of that paper interpret as consistent with long-term effects of low levels of infant-directed speech [@cristia2020infant]. However, @cristia2020infant also point out that this is based on between-paper comparisons, and thus methods and myriad other factors have not been controlled for. The Yélî community can help us gain new insights into this matter because direct speech to children under 3;0 is comparably infrequent in this community [in fact it may be infrequent in many settings, including urban ones @bunceURcrosscultural], and additionally shares other societal characteristics wih the Tsimane' [e.g., is rural and relies on farming, children grow up in wide familial networks, etc; @casillas2021early]. Although infant-directed speech has been measured in different ways among the Tsimane' and the Yélî communities, our most comparable estimates at present suggest that Tsimane' young children are spoken to about 4.2 minutes per hour [@scaff2021daylong], and Yélî children about 3.6 minutes per hour [@casillas2021early]. Thus, if these input quantities in early childhood relate to lower NWR scores later in life, we should observe similarly low NWR scores here as in @cristia2020infant.

@@

kable(stims.wide,
  "latex", booktabs = T,
  caption="NWR stimuli in orthographic (Orth.) and phonological (Phon.) representations.",
  row.names =F) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  add_header_above(c("Practice" = 2, "Monosyll" = 2,
    "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))

@@

The first author then annotated the onset and offset of all children's productions from the audio recording using Praat audio annotation software [@Praat], then ran a script to extract these tokens, pairing them with their original auditory target stimulus, and writing these audio pairs out to .wav clips. The assistant then listened through all these paired target-repetition clips randomized across children and repetitions, grouped such that all the clips of the same target were listened to in succession. For each clip, the assistant indicated in a notebook whether the child production was a correct or incorrect repetition and orthographically transcribed the production, noting when the child uttered a recognizable word or phrase and adding the translation equivalent of that word/phrase into English. The assistant was also provided with some general examples of the types of errors children made without making specific reference to Yélî sounds or the items in the elicitation sets. Because the phonological inventory is so acoustically packed and annotation was done based on audio data alone, it might be easy to misidentify a segment. Therefore, the assistant double-checked all of her annotations by listening to them and assessing them a second time, once she had completed a full first round.

@@

item.plot <- ggplot(data = xling, aes(x = Avg_fr, y = Word, label = phono)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  geom_text(family = "Doulos SIL") +
  ylab("NWR scores (% words)") +
  xlab("Average cross-linguistic phone frequency") +
  theme_apa()
ggsave("nwr.by.freq.ITEM.png", dpi = 300, device = png())
knitr::include_graphics("nwr.by.freq.ITEM.png")
#dev.off()
```

Additionally, the effect for the interaction between the two fixed effects was small but significant (ß = `r mycoeff["avg_fr_s:age.rounded_s","Estimate"]`, SE ß = `r mycoeff["avg_fr_s:age.rounded_s","Std. Error"]`, p `r pval.display(mycoeff["avg_fr_s:age.rounded_s","Pr(>|z|)"])`): The effect of frequency was larger for older children. Inspection of Figure \@ref(fig:fig-xling-freq-age3) suggests that the age effects are more marked for items containing cross-linguistically common phones, such that children's average performance increases more rapidly with age for those than for items containing cross-linguistically uncommon phones.

```{r fig-xling-freq-age3, fig.pos = "!t", fig.align = "center", out.width = '65%', fig.cap="NWR scores as a function of age and typological frequency. Lines are fits from the model in the main text predicting NWR scores from child age (x axis) and the average frequency with which each phone is found across languages (mean, or plus/minus one standard deviation). Each circle indicates the estimated NWR scores for one child at one frequency level."}

@@

plot_model(xl_fr, type = "pred", terms = c("age.rounded_s","avg_fr_s")) +
  geom_point(data = trnsc.inc.indivs, inherit.aes = FALSE,
             aes(x = age.rounded_s, y = correct, color = factor(avg_fr_s))) +
  scale_color_manual(values = c("red", "orange", "green"),
                     labels = c("mean - 1sd", "mean", "mean + 1sd")) +
  scale_fill_manual(values = c("red", "orange", "green"),
                    guide = FALSE) +
  labs(color = "Average\nfrequency\nscore",
       y = "% Correct", x = "Child age\n(standardized)") +
  theme_apa() +
  theme(plot.title = element_blank(),
        legend.key = element_rect(color = "white")) +
  guides(color = guide_legend(override.aes = list(fill = NA), reverse = TRUE))

@@

@@

read.table("substitution_bank.txt",header=T)->sub_bank_full
sub_bank=sub_bank_full[,1:2]
sub_bank$target=factor(sub_bank$target,levels=allVC)
sub_bank$realization=factor(sub_bank$realization,levels=allVC)

@@

read.table("deletion_bank.txt",header=T)->del_bank_full
del_bank=del_bank_full[,1]
del_bank=factor(del_bank,levels=allVC)
del_tab= table(del_bank)[allVC]

read.table("match_bank.txt",header=T)->match_bank_full
match_bank=match_bank_full[,1]
match_bank=factor(match_bank,levels=allVC)
match_tab= table(match_bank)[allVC]

@@

We do not have the necessary data to assess whether the correlation is indeed weaker for Yélî Dnye learners than learners of other languages, but we did find a robust correlation of average segmental cross-linguistic frequency and NWR performance: Even accounting for age and random effects of item and participant, we saw that target words with typologically more common segments were repeated correctly more often. This effect was large, with a magnitude more than twice the size of the effect of participant age. Additionally, we observed an interaction between age and this factor, which emerged because cross-linguistic frequency explained more variance at older ages (i.e., the difference in performance for more versus less typologically frequent sounds was greater for older than younger children). Importantly, the correlation between performance and typological frequency  remained significant  after accounting for the frequencies of these segments in a conversational corpus. An analysis of the substitutions made by children also aligned with this interpretation, with typologically more common sounds being substituted for typologically less common ones.

### 2021-10-27 manuscript.tex
version ready for proofing

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NWR in Yélî Dnye learners}
\keywords{phonology, non-word repetition, Papuan, non-industrial, non-urban, comparative, typology, markedness, literacy\newline\indent Word count: ~11,500 words}
\usepackage{lineno}

@@

Our focus on age stems from previous work, where performance increases with child age (Farmani et al., 2018; Kalnak, Peyrard-Janvid, Forssberg, \& Sahlén, 2014; Vance, Stackhouse, \& Wells, 2005). Although past research has not investigated potential correlations with birth order on NWR, there is a sizable literature on these correlations in other language tasks (e.g., Havron et al., 2019), and therefore we report on these too. Common explanations for advantages for first- over later-born children include differential allocation of familial resources, particularly parental behaviors of cognitive stimulation (Lehmann, Nuevo-Chiquero, \& Vidal-Fernandez, 2018). Regarding child sex, no significant correlation has been found in previous NWR research (Chiat \& Roy, 2007), and in other language tasks evidence is mixed. Finally, prior research varies on whether significant differences as a function of maternal education are reported (Balladares, Marshall, \& Griffiths, 2016; e.g., no difference found in Farmani et al., 2018; Kalnak, Peyrard-Janvid, Forssberg, \& Sahlén, 2014; Meir \& Armon-Lotem, 2017; Santos, Frau, Labrevoit, \& Zebib, 2020; whereas differences were reported in Tuller et al., 2018). In other lines of work, maternal education correlates with child language outcomes, including vocabulary reports (Frank, Braginsky, Yurovsky, \& Marchman, 2017) and word comprehension studies (Scaff, 2019). The causal pathways explaining this correlation are complex, but one explanation that is often discussed involves more educated mothers talking more to their children (see discussion in Cristia, Farabolini, Scaff, Havron, \& Stieglitz, 2020).

@@

@@

The first author then annotated the onset and offset of all children's productions from the audio recording using Praat audio annotation software (Boersma \& Weenink, 2020), then ran a script to extract these tokens, pairing them with their original auditory target stimulus, and writing these audio pairs out to .wav clips. The assistant then listened through all these paired target-repetition clips randomized across children and repetitions, grouped such that all the clips of the same target were listened to in succession. For each clip, the assistant indicated in a notebook whether the child production was a correct or incorrect repetition and orthographically transcribed the production, noting when the child uttered a recognizable word or phrase and adding the translation equivalent of that word/phrase into English. The assistant was also provided with some general examples of the types of errors children made without making specific reference to Yélî sounds or the items in the elicitation sets. Because the phonological inventory is so acoustically packed and because annotation was done based on audio data alone, it might be easy to mis-identify a segment, the assistant double-checked all of her annotations by listening to them and assessing them a second time, once she had completed a full first round.

@@

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

Additionally, the effect for the interaction between the two fixed effects was small but significant (ß = 0.22, SE ß = 0.09, p = 0.01): The effect of frequency was larger for younger children. Inspection of Figure \ref{fig:fig-xling-freq-age3} suggests that the age effects are more marked for items containing cross-linguistically common phones, such that children's average performance increases more rapidly with age for those than for items containing cross-linguistically uncommon phones.

@@

\caption{Model predicting NWR scores from child age (x axis) and the average frequency with which each phone is found across languages (mean, or plus/minus one standard deviation).}\label{fig:fig-xling-freq-age3}
\end{figure}

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NWR in Yélî Dnye learners}
\keywords{phonology, non-word repetition, Papuan, non-industrial, non-urban, comparative, typology, markedness, literacy\newline\indent Word count: ~12,200 words}
\usepackage{lineno}

@@

Our focus on age stems from previous work, where performance increases with child age (Farmani et al., 2018; Kalnak, Peyrard-Janvid, Forssberg, \& Sahlén, 2014; Vance, Stackhouse, \& Wells, 2005). Although past research has not investigated potential correlations with birth order on NWR, there is a sizable literature on these correlations in other language tasks (e.g., Havron et al., 2019), and therefore we report on these too. Common explanations for advantages for first- over later-born children include differential allocation of familial resources, particularly parental behaviors of cognitive stimulation (Lehmann, Nuevo-Chiquero, \& Vidal-Fernandez, 2018). Regarding child sex, no significant correlation has been found in previous NWR research (Chiat \& Roy, 2007), and in other language tasks evidence is mixed. Finally, prior research varies on whether significant differences as a function of maternal education are reported. For instance, no significant difference was found some studies (Balladares, Marshall, \& Griffiths, 2016; Farmani et al., 2018; Kalnak, Peyrard-Janvid, Forssberg, \& Sahlén, 2014; Meir \& Armon-Lotem, 2017); whereas significant differences were reported in others (Santos, Frau, Labrevoit, \& Zebib, 2020; Tuller et al., 2018). In other lines of work, maternal education correlates with child language outcomes, including vocabulary reports (Frank, Braginsky, Yurovsky, \& Marchman, 2017) and word comprehension studies (Scaff, 2019). The causal pathways explaining this correlation are complex, but one explanation that is often discussed involves more educated mothers talking more to their children (see discussion in Cristia, Farabolini, Scaff, Havron, \& Stieglitz, 2020).

@@

\begin{table}[H]

@@

The first author then annotated the onset and offset of all children's productions from the audio recording using Praat audio annotation software (Boersma \& Weenink, 2020), then ran a script to extract these tokens, pairing them with their original auditory target stimulus, and writing these audio pairs out to .wav clips. The assistant then listened through all these paired target-repetition clips randomized across children and repetitions, grouped such that all the clips of the same target were listened to in succession. For each clip, the assistant indicated in a notebook whether the child production was a correct or incorrect repetition and orthographically transcribed the production, noting when the child uttered a recognizable word or phrase and adding the translation equivalent of that word/phrase into English. The assistant was also provided with some general examples of the types of errors children made without making specific reference to Yélî sounds or the items in the elicitation sets. Because the phonological inventory is so acoustically packed and annotation was done based on audio data alone, it might be easy to misidentify a segment. Therefore, the assistant double-checked all of her annotations by listening to them and assessing them a second time, once she had completed a full first round.

@@

Additionally, the effect for the interaction between the two fixed effects was small but significant (ß = 0.22, SE ß = 0.09, p = 0.01): The effect of frequency was larger for older children. Inspection of Figure \ref{fig:fig-xling-freq-age3} suggests that the age effects are more marked for items containing cross-linguistically common phones, such that children's average performance increases more rapidly with age for those than for items containing cross-linguistically uncommon phones.

@@

\caption{NWR scores as a function of age and typological frequency. Lines are fits from the model in the main text predicting NWR scores from child age (x axis) and the average frequency with which each phone is found across languages (mean, or plus/minus one standard deviation). Each circle indicates the estimated NWR scores for one child at one frequency level.}\label{fig:fig-xling-freq-age3}
\end{figure}
